---
title: "Rpackage for 'Integrated Depth for Partially Observed Functional Data'"
author: "Elías, Antonio, Jiménez, Raúl, Paganoni, Anna M. and Sangalli, Laura M."
date: "22/12/2020"
output:
  md_document:
    variant: markdown_github
---

```{r setup, include=FALSE, message = FALSE, warning = FALSE, fig.align = 'center'}
knitr::opts_chunk$set(echo = TRUE)
library(POIFD)
```

POIFD
=======

<!-- badges: start -->
[![License](https://img.shields.io/badge/license-GPL%20v3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0)
[![Travis build status](https://travis-ci.com/aefdz/dbPoFDA.svg?branch=master)](https://travis-ci.com/aefdz/dbPoFDA)
<!-- badges: end -->

## Overview

Software companion for the paper “Integrated Depth for Partially Observed Functional Data” (Elías, Antonio, Jiménez, Raúl, Paganoni, Anna M. and Sangalli, Laura M., 2020). 

It implements the proposed depth measures, functional boxplot and functional outliergram for partially observed functional data. 

## Installation 

```{r, eval = FALSE}
#install the package
devtools::install_github("aefdz/POIFD")

#load the package
library(POIFD)
```

## Test usage

```{r, fig.align="center"}
#Generate data
sparse_gaussian <- gaussian_PoFD(n=10, p=200, type="sparse", observability=0.5)
common_gaussian <- gaussian_PoFD(n=10, p=200, type="common", observability=0.5)
interval_gaussian <- gaussian_PoFD(n=10, p=200, type="interval", ninterval=3, observability=0.5)

#plot the data sets
plot_sparse <- plot_PoFD(sparse_gaussian$pofd)
plot_interval <- plot_PoFD(interval_gaussian$pofd)
plot_common <- plot_PoFD(common_gaussian$pofd)

plot_sparse 

plot_interval

plot_common
```


### Computing depths

```{r}
mbd <- POIFD(common_gaussian$pofd, type = "MBD")

(median <- mbd[1])
```

- Fraiman, R. and Muniz, G. (2001).  Trimmed means for functional data. *Test*, 10(2):419–440.
- López-Pintado,  S.  and  Romo,  J.  (2009).   On  the  concept  of  depth  for  functional  data. *Journal of the American Statistical Association*, 104(486):718–734.
- López-Pintado, S. and Romo, J. (2011).  A half-region depth for functional data. *Computational Statistics and Data Analysis*, 55(4):1679–1695.

### Functional Boxplot and magnitude outliers

```{r, fig.align="center"}
data(exampleData)

fboxplot <- boxplot_PoFD(exampleData$PoFDextremes_outliers, centralRegion = 0.5, fmag = 1.5, fdom = 1)

fboxplot$magnitude
fboxplot$domain

fboxplot$fboxplot

```

- Sun,  Y.  and  Genton,  M.  G.  (2011).   Functional  boxplots. *Journal  of  Computational and Graphical Statistics*, 20(2):316–334.

### Functional Outliergram and Shape Outliers

```{r , fig.align="center"}
outliergram <- outliergram_PoFD(exampleData$PoFDextremes_outliers)

outliergram$shape

outliergram$outliergram

```

- Arribas-Gil, A. and Romo, J. (2014).  Shape outlier detection and visualization for functional data:  the outliergram. *Biostatistics*, 15(4):603–619.

## References

Elías, Antonio, Jiménez, Raúl, Paganoni, Anna M. and Sangalli, Laura M. (2020). Integrated Depths for Partially Observed Functional Data. (submitted) 
