---
title: "Illustration of the simulations"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Illustration of the simulations}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

## Load packages
```{r}
library("fdaPOIFD")
```

## Generate data

```{r}
N <- 100
P <- 200
dataPOFD <- gaussian_PoFD(n=N, p=P, type = "common", observability = 0.2)
```

## Depth computations

### Depth on fully observed data
```{r}
depth_complete <- POIFD(dataPOFD$fd, type = "MBD")
```
Notice that the function POIFD on fully observed data coincides with the unweighted IFD.

### POIFD 
```{r}
depth_POIFD <- POIFD(dataPOFD$pofd, type = "MBD")
```

### Depth with reconstructed curves by Goldsmith (2013)
Install and load the Rpackage *refund*.

```{r}
library("refund")

Fit.IV <- ccb.fpc(t(dataPOFD$pofd), n.boot = 10)

goldsmith_reconstruction <- t(Fit.IV$Yhat)
depth_goldsmith <- POIFD(goldsmith_reconstruction, type = "MBD")
```

Notice that the function POIFD on reconstructed data coincides with the unweighted IFD.

### Depth with reconstructed curves by Kraus (2015)
Kraus (2015) was implemented using the function *pred.missfd* obtained from the code at [https://is.muni.cz/www/david.kraus/web_files/papers/partial_fda_code.zip](https://is.muni.cz/www/david.kraus/web_files/papers/partial_fda_code.zip).

### Depth with reconstructed curves by Liebl (2020)

Liebl (2020) was implemented using the function *reconstructKneipLiebl* obtained from the code at [https://github.com/lidom/ReconstPoFD](https://github.com/lidom/ReconstPoFD)
